### 2023-03-29 resilience-safe-down.tex
details

\begin{theorem}
The resilience problem is decidable for WSTS with 
%	more than one minimal element, 
$\Safe=\downarrow \Safe$
and $\Bad=\uparrow \Bad$
and
\textcolor{red}{
additional hypothesis.
}
\end{theorem}

@@

Let's assume for now for simplicity's sake that $\Bad = \uparrow \{b\}$

@@

Resilience asks whether 
$ \uparrow \{b\} \subseteq J'_1 \cup J'_2 \cup ... \cup J'_n$.

Of note is that $ \downarrow \{b\} \subseteq J'_1 \cup J'_2 \cup ... \cup J'_n$
if and only if
there exists some $i$ such that
$\downarrow \{b\} \subseteq J'_i$.

>>>>

\begin{theorem}
The resilience problem is decidable for WSTS with 
%	more than one minimal element, 
$\Safe=\downarrow \Safe$
and $\Bad=\uparrow \Bad$
and
\textcolor{red}{
additional hypothesis.
}
\alain{est-ce que  $\pred(D)$ is downward closed avec D downward closed serait suffisant ? si l'ordre est omega2 alors closbas+inclusion est wqo donc il faudrait juste que la suite croissante $pred^n(D)+le reste$ converge...}
\end{theorem}

@@

Let's assume for now for simplicity's sake that $\Bad = \uparrow b$

@@

Resilience asks whether 
$ \uparrow b \subseteq J'_1 \cup J'_2 \cup ... \cup J'_n$.

Of note is that $ \downarrow b \subseteq J'_1 \cup J'_2 \cup ... \cup J'_n$
if and only if
there exists some $i$ such that
$\downarrow b \subseteq J'_i$.
